{\LARGE \textsc{Biotic invasions reduce the manageability of mutualistic networks}}

### 2017-05-04 paper/response_to_reviewers.Rmd

We agree with the handling editor that the most notable assumption of our approach is that it is based on a linear approximation of the dynamics of the system. 
Naturally, it is important to take this into account when applying the framework. 
We disagree, however, with the conclusion that this detail renders the approach ecologically irrelevant.

We will approach the editor's comments in two stages below. 
First, we will argue that linear models can be useful to describe the dynamics of ecological communities and pollination communities in particular. 
Second, we believe that the editor's observations potentially arises from our failure to clearly delineate the scope and goals of our study.
Therefore, we then provide some further clarification in this regard and to the aims of structural controllability in general. 
Finally, we provide a detailed account of the edits we have made in the manuscript in order to prevent this kind of misunderstanding going forward.

While ecological systems are inherently non-linear, variations of Lokta-Volterra and other models with linear functional responses have been widely used in ecology to describe both multitrophic ecological communities [@Heckmann2012; @Heath2014] and mutualistic pollination networks [@Lever2014; @Rohr2014; @Valdovinos2016]. 
Importantly, several studies have found that, despite the lack of "realism", parametrizations with linear responses still provide a valuable starting point to investigate community stability [@Tang2014], population size [@Mackinson2003], and relative species importance [@Zhao2016]. 
Similarly, we view the structural controllability as a *starting point* to investigate the way ecological communities could be steered from an equilibrium point to another in an informed fashion.

As noted in our manuscript, the dynamics of an ecological system near equilibrium can be represented by $\frac{dx}{dt} = \mathbf{A}x(t) + \mathbf{B}u(t)$. 
Here, $\mathbf{B}$ is the "input matrix" and $u(t)$ is the control vector. 
The matrix $\mathbf{B}$ has size $S \times D$, where $S$ is the number of species in the community and $D$ is the number of species whose abundances are modified by the control vector. 
The editor points out that a structural-controllability approach would not be useful in linear ecological systems because it will be "only valid in an infinitesimal border" around an initial equilibrium point. 
This comment would be completely appropriate if our aim were to design the time-varying control trajectory that drives the system from one equilibrium point another. 
In other words, it would be wrong to design $u(t)$ based exclusively on a local linear approximation at the initial equilibrium. 
Our manuscript, however, has a completely different aim.

### 2017-05-04 paper/drafts_and_revisions/submission_2016Jul11/covering_letter_dbs_2016-07_12.tex
Change folder names

Central to this manuscript is the introduction, development, and application of the theoretical concept of \textbf{ecological manageability}.
Based on the patterns of interactions between species, this idea can provide two main pieces of information. 
First, it allows to quantify the \textit{community manageability}---an indication of the difficulty of controlling the abundances of all species in the community. 
Second it allows to identify \textit{driver species}--- those species with a disproportionate ability to alter other species' abundances.  
Here, we use this concept as a framework to study the changes induced by biotic invasions to pollination networks.

Multiple empirical observations have suggested that the structural changes caused by invasions may lead to increased ecosystem resilience. 
Our study is the first to use empirical data to provide theoretical support for this idea. 
Furthermore, our approach to identify driver species and quantify their relative importance, is unique in that it is based directly on the aspects of network structure that determine the behavior of the community as a holistic dynamical system. 
Our results also highlight the extent to which some species---invaders in particular---can drive the dynamics of other species across their community, and also identify ``asymmetric dependence'' as the potential mechanism driving the interspecific differences.

Despite our focus, understanding how drivers of ecosystem change affect ecosystem dynamics is not exclusive to mutualistic communities. 
Indeed, we envisage the application of the concepts we introduce to answer a wide range of ecological questions in communities structured by different types of interactions.
As such, we have sought to highlight the methodology necessary for its implementation---an extension of recently developed tools at the interface of complex systems and control theory---thoroughout the manuscript.

Our study fundamentally lies within ecological theory, yet it has ramifications pertinent to ecological application. 
Indeed, we show in the paper that concepts like ``manageability'' have the potential to stimulate much needed research that reduce the gap between theory and management.
Hopefully our study and more like it will set us on the track to informed, rather than hopeful, ecosystem interventions.

Lastly, please note that the enclosed work represents a novel contribution for all co-authors involved and no related work published, in press, or submitted during this or last year has been cited.

>>>>

Central to this manuscript is the introduction, development, and application
of the theoretical concept of \textbf{ecological manageability}. Based on the
patterns of interactions between species, this idea can provide two main
pieces of information. First, it allows us to quantify the \textit{community
manageability}---an indication of the difficulty of controlling the abundances
of all species in the community. Second it allows to identify \textit{driver
species}--- those species with disproportionate ability to alter other
species' abundances. Here, we use this concept as a framework to study the
changes induced by biotic invasions to pollination networks.

Multiple empirical observations have suggested that the structural changes
caused by invasions may lead to increased ecosystem resilience. Our study is
the first to use empirical data to provide strong theoretical support for this
idea. Furthermore, our approach to identify driver species and quantify their
relative importance is unique in that it is based directly on the aspects of
network structure that determine the behavior of the community as a holistic
dynamical system. Our results also highlight the extent to which some
species---invaders in particular---can drive the dynamics of other species
across their community, and also identify ``asymmetric dependence'' as the
potential key mechanism driving the interspecific differences.

Despite our focus, understanding how drivers of ecosystem change affect
ecosystem dynamics is not exclusive to mutualistic communities. Indeed, we
envisage the application of the concepts we introduce here to answer a wide
range of ecological questions in communities structured by different types of
interactions. As such, we have sought to highlight the methodology necessary
for its implementation---an extension of recently developed tools at the
interface of complex systems and control theory---thoroughout the manuscript.

While our study fundamentally lies within ecological theory, we cannot
overlook its relevance to ecological applications. Indeed, we demonstrate in
the paper itself that concepts like ``manageability'' have the potential to
stimulate much needed research that shortens the gap between theory and
management. Hopefully our study and more like it will set us on the track to
informed, rather than hopeful, ecosystem interventions.

Lastly, please note that the enclosed work represents a novel contribution for
all co-authors involved and no related work published, in press, or submitted
during this or last year has been cited therein.
